\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-21 doc/sw-system.tex
Even though I need to rerun to make the roc and purity curves, I might as well commit these changes

Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly 
detected sims divided by the total number of sims in the training set, while
purity is the number of the number of correctly detected sims divided by the
number of detections that would be claimed in a realistic sample. The purity
can only be calculated approximately. First we compute the expected number of
false positives by multiplying the FPR by the expected number of non-lenses in
the survey. Then we multiply the TPR by the expected number of lenses in the
survey, to get the expected number of true positives. The sum of the true
positives and the false positives gives the expected sample size; dividing the
expected number of true positives by this sample size gives the purity.

\todo{Chris}{Make completeness vs purity plot and add it here, please!}

>>>>

Adopting the online stage 1 analysis, and the offline stage 2 analysis, we show
in \Fref{fig:results:sample:CP} a plot of completeness versus purity in the two
stages. As in \Fref{fig:results:sample:roc}, the detection threshold varies
along the curves. Completeness is defined as the number of correctly detected
sims divided by the total number of sims in the training set, while purity is
the number of correct detections divided by the total number of detections.
\footnote{The completeness is equivalent to the TPR and is also known elsewhere
as the `recall'. The purity is also known as the `precision'.} If the training
set samples from the same systems as the test set, then the completeness of the
training set will be equivalent to the completeness of the test set. The purity
depends on the proportion of sims to duds, and so the purity of the test set
must be approximated by rescaling the training set to the expected proportion
of lens systems to not-lens systems in the survey.  First we compute the
expected number of false positives by multiplying the FPR by the expected
number of non-lenses in the survey. Then we multiply the TPR by the expected
number of lenses in the survey, to get the expected number of true positives.
The sum of the true positives and the false positives gives the expected sample
size; dividing the expected number of true positives by this sample size gives
the purity. Note that the completeness is invariant to this transformation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
\caption{Completeness-estimated purity curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
